Exception Handling Bug Hazards in Android

### 2015-10-08 SPRINGER_JOURNAL/msr_journal.tex
coders sentence

\noindent\emph{\textbf{RQ 2.2: How do the NullPointerExceptions impact the development of robust Android apps?}}

@@

\noindent\emph{\textbf{RQ 2.3: How do Cross-Type Wrappings impact the development of robust Android apps?}}

@@

\bigskip
\noindent\emph{\textbf{RQ 2.4: Are developers aware of the robustness threats caused by JNI undocumented checked exceptions?}}
\bigskip

@@

%\noindent\emph{\textbf{Q2: Do developers know about exception handling best practices?}}
%We can observe that 62\% of surveyed Android developers follow Java exception handling best 
%practices. Among the best practices cited by developers the most popular ones were: avoid generic 
%catches and avoid empty catch blocks. They did not mention a any guide or reference of best practices. 
%When asked about best practices specific to Android developers, most of the developers mentioned that 
%they did no about them. The ones who answered positively said that they adopt the same best practices 
%as in any Java program.

\noindent\emph{\textbf{RQ 2.5: How does the exception handling code affect the development of robust apps and how do developers prevent apps from crashing?}}

>>>>

\noindent\emph{RQ 2.2: How do the NullPointerExceptions impact the development of robust Android apps?}

@@

\bigskip 
%\textbf{
\noindent\emph{RQ 2.3: How do Cross-Type Wrappings impact the development of robust Android apps?}

@@

\bigskip
\noindent\emph{RQ 2.4: Are developers aware of the robustness threats caused by JNI undocumented checked exceptions?}
\bigskip

@@

%\noindent\emph{Q2: Do developers know about exception handling best practices?}
%We can observe that 62\% of surveyed Android developers follow Java exception handling best 
%practices. Among the best practices cited by developers the most popular ones were: avoid generic 
%catches and avoid empty catch blocks. They did not mention a any guide or reference of best practices. 
%When asked about best practices specific to Android developers, most of the developers mentioned that 
%they did no about them. The ones who answered positively said that they adopt the same best practices 
%as in any Java program.

\noindent\emph{RQ 2.5: How does the exception handling code affect the development of robust apps and how do developers prevent apps from crashing?}
